---
title: "Introduction to Shiny"
author: "George & Wush"
date: '`r Sys.Date()`'
output:
  ioslides_presentation:
    #css: css/ioslides.css
    #logo: assets/img/Taiwan-R-logo.png
    widescreen: yes
subtitle: shiny
runtime: shiny
---

# 傢伙準備好

## 環境安裝

R 套件安裝
```{r Surround, eval=FALSE}
install.packages(c("dplyr","ggplot2","shiny","devtools"))
devtools::install_github('rstudio/shinyapps')
```
```{r echo=FALSE,eval=FALSE}
sessionInfo()
```


## What is Shiny?

- Web Application Framework for R
- Reactive Programming (Interactive user interfaces)
- Default UI theme Bootstrap (Twitter Bootstrap)
- Support HTML/CSS/JavaScript/Markdown
- Provided by RStudio from 2012-11 Beta
- Until now 2015-05 v0.11

## Why Choosing Shiny

- Let R User become a simple web designer/devoleper  
- Using R language then you can create web app  
    - know more about HTML/CSS/Javascript will be better  
- Support HTML element  
    - Input: select, checkbox, radio, etc...  
    - Output: text, table, plot, etc...  

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```
